Increasing the mortality gap? Social inequality in mortality among elderly and adults in Northern Sweden 1851--2013\footnote{Session "Health, morbidity, and mortality" at the Nordic Demographic Symposium 14--16 June 2017, Turku, Finland}

### 2017-06-12 abo.Rnw
Correcting title in final version

\title{Long--term perspectives of social inequality in mortality among adults and elderly in
  northern  Sweden 1851--2013\footnote{Session "Health, morbidity, and mortality" at the Nordic Demographic Symposium 14--16 June 2017, Turku, Finland}
}

>>>>

\title{Increasing the mortality gap? Social inequality in mortality among elderly and adults in
  Northern  Sweden 1851--2013\footnote{Session "Health, morbidity, and mortality" at the Nordic Demographic Symposium 14--16 June 2017, Turku, Finland}
}
